Deep and Shallow Types for Gradual Languages

### 2022-05-21 g-pldi-2022/camera-tex/paper.tex
pldi: ack neu funding (how to ack 2nd affiliation?)

This work is supported by NSF grant 2030859 to the CRA for the
\href{https://cifellows2020.org}{CIFellows} project.
Thanks to Matthias Felleisen for improving drafts of this paper and to
the rest of my thesis committee for supervising parts of this work:
Amal Ahmed,
Fritz Henglein,
Shriram Krishnamurthi,
Sam Tobin{-}Hochstadt,
and
Jan Vitek.

>>>>

This work is supported by
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1518844}{NSF grant 1518844}
and
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2030859}{NSF grant 2030859}
to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
Thanks to Matthias Felleisen for improving drafts of this paper and to
the rest of my thesis committee for supervising parts of this work:
Amal Ahmed,
Fritz Henglein,
Shriram Krishnamurthi,
Sam Tobin{-}Hochstadt,
and
Jan Vitek.
